### 2015-01-14 src/methodology.Rnw
update methodlogy

\subsubsection{Sampling over program elements and variants}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope is just x\% selection).

We used the formula by Zhang et al.~\cite{zhang2013ase},
\[sample(x) = \lfloor x + random(0..1) \rfloor \]
to correctly sample decimal numbers.
Next, we slightly modified this criteria, and instead of
\textit{sample()} which uses probability to manage the decimal numbers,
we applied \textit{round()} to obtain the nearest whole number, which
was used as the number of samples to be chosen from the population.
The new strategy ignores program elements with small number of mutants.
This strategy can potentially guide mutation generation toward more
complex program elements.
That is, if the number of mutants dropped below a threshold determined by
the mutant reduction ratio, that program element would not contribute any
mutants to the final result.  Conceptually the idea is that mutants of more
complex code have more discriminatory power (and may correspond better to
real faults --- though we do not evaluate this concept).

Next, we explored in the other direction, by forcing the program elements
to return at least one element by using \textit{ceil()}. That is,
irrespective of the fraction being sampled, the simplest elements always
contributed at least one mutant to the total sample, ensuring coverage but
also giving priority to complex elements.

\subsubsection{Lines per element and variants}
Our previous research~\cite{gopinath2014code} found that statement coverage
was highly correlated with mutation score for a project. This immediately
suggests that perhaps choosing one mutant per line may be sufficient to achieve
a close approximation of the final mutation score. Further, statement deletion
has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
has been found to reduce the number of mutants well, with negligible
decrease in effectiveness. This also provides a nice comparison with similar
numbers of mutants between operator selection and random sampling of mutants.

We extended sampling to levels coarser than methods, i.e. method, class, and
project. We sampled $n$ mutants from a method (class or project), where $n$
is the number of statements in the method (class or project).

This provided a test of the hypothesis of how important a mutation sampling's
relationship to simple code coverage is. This was extended to class and
project scope also.

For the first variant, we applied the x\% sampling to the result of
the first sampling based on line counts. That is, in the case of
methods, we first selected \textit{linecount} mutants each from each
method, and applied the x\% selection to this result.
For example, for $1/2$ sampling on methods if one method had
$10$ lines and another had $20$, we sampled $10$ mutants from
the first, and $20$ from the second, and from the combined
$30$ mutants, we sampled $15$.  For the second variant, we did the
sampling in one go, where we chose \textit{linecount/x} number of
mutants from each program element.  That is, in the previous example,
only $5$ mutants from the first and $10$ mutants from the second
method would be chosen.

@@

>>>>

@@

\subsubsection{Sampling over program elements}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope is just x\% selection).

We used the formula by Zhang et al.~\cite{zhang2013ase},
\[sample(x) = \lfloor x + random(0..1) \rfloor \]
to correctly sample decimal numbers.
